---
title: "Projek UAS"
author: "Elisabeth Lumban Tobing"
date: "2023-05-26"
output: html_document
---

```{r setup, include=FALSE}
install.packages("dplyr")
update.packages(ask = FALSE)
install.packages("rlang")

update.packages("rlang")
install.packages("rlang")
lulus_UPT <- readxl::read_excel("Projek UAS.xlsx", sheet = "Sheet1")
str(lulus_UPT)
```

Pemeriksaan awal data dalam Faktor Kelululusan Ujian Masuk Perguruan Tinggi (UPT)

```{r cars}
##untuk melihat ringkasan atau merangkum data
summary(lulus_UPT)
lulus_UPT

##untuk mellihat struktur data
head(lulus_UPT)
str(lulus_UPT)
tail(lulus_UPT)
```
Proses pengelempokkan data yang dibagi dalam bentuk variabel independent dan variabel dependent

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r pressure, echo=FALSE}

```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r pressure, echo=FALSE}
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r pressure, echo=FALSE}
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r pressure, echo=FALSE}
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r pressure, echo=FALSE}
```